SDR enhancement by clouds

### 2024-03-20 article/article.tex
Commit 2024-03-20 17:12

{\centering \includegraphics[width=0.7\linewidth]{../images/P_daily_trend-1}

@@

{\centering \includegraphics[width=0.7\linewidth]{../images/P_energy-7}

@@

{\centering \includegraphics[width=0.7\linewidth]{../images/P_energy-6}

@@

{\centering \includegraphics[width=0.7\linewidth]{../images/P_energy-5}

@@

{\centering \includegraphics[width=0.7\linewidth]{../images/P_energy-8}

@@

{\centering \includegraphics[width=0.7\linewidth]{../images/clim_CE_month_norm_MAX_median_N-2}

@@

{\centering \includegraphics[width=0.7\linewidth]{../images/P-relative-distribution-diff-1}

@@

{\centering \includegraphics[width=0.7\linewidth]{../images/groups-1}

@@

{\centering \includegraphics[width=0.7\linewidth]{../images/P-groups-bin2d-1}

@@

{\centering \includegraphics[width=0.7\linewidth]{../images/clim_ECE_month_norm_MAX_median_N-2}

@@

{\centering \includegraphics[width=0.7\linewidth]{../images/extremedistributions-2}

>>>>

{\centering \includegraphics[width=0.6\linewidth]{../images/P_daily_trend-1}

@@

{\centering \includegraphics[width=0.6\linewidth]{../images/P_energy-7}

@@

{\centering \includegraphics[width=0.6\linewidth]{../images/P_energy-6}

@@

{\centering \includegraphics[width=0.6\linewidth]{../images/P_energy-5}

@@

{\centering \includegraphics[width=0.6\linewidth]{../images/P_energy-8}

@@

{\centering \includegraphics[width=0.6\linewidth]{../images/clim_CE_month_norm_MAX_median_N-2}

@@

{\centering \includegraphics[width=0.6\linewidth]{../images/P-relative-distribution-diff-1}

@@

{\centering \includegraphics[width=0.6\linewidth]{../images/groups-1}

@@

{\centering \includegraphics[width=0.6\linewidth]{../images/P-groups-bin2d-1}

@@

{\centering \includegraphics[width=0.6\linewidth]{../images/clim_ECE_month_norm_MAX_median_N-2}

@@

{\centering \includegraphics[width=0.6\linewidth]{../images/extremedistributions-2}
